---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# obt

<!-- badges: start -->
[![R-CMD-check](https://github.com/grousell/obt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/grousell/obt/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of Ontario Board Tools (obt)) is to provide data professionals in Ontario school boards (and elsewhere) tools to assist with data cleaning and analyses of commonly used data sets. These include:
- Elementary and Secondary Report Card
- EQAO

## Installation

You can install the development version of obt from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("grousell/obt")
```

## Recode Report Card Marks to Achievement Levels 

This functions takes a vector of report card marks and re-codes into Ontario achievement levels. 
```{r recode_reportcard_to_levels, warning=FALSE, message=FALSE}
library(obt)
library(dplyr)
df <- ele_rc

df |>
  select (id, reading) |> 
  mutate (reading_level = obt_recode_rc_to_levels(reading))
  
```

## Summary Table

This function provides a summary table of counts and percentages for either a single variable, or a grouped variable. This table can then be used directly with `ggplot2` for visualisations. 
```{r summary_table}
library(obt)

df <- ele_rc

df |> 
  obt_summary_table(school)

```

## Grouped Summary Table

```{r grouped_summary_table}
library(obt)

df <- ele_rc

df |> 
  obt_summary_table(school, grade)

```
