---
title: "obt"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{obt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of the `obt` package is to provide tools for data professionals in Ontario school boards (and elsewhere) to work with common data sets across the province. This includes:  

* Report Card Data (elementary and secondary)  
* EQAO Data (Primary and Junior assessments of Reading, Writing and Mathematics, Grade 9 Assessments of Mathematics and the Ontario Secondary School Literacy Test) (pending)   
* Ontario University Application Center (OUAC) and Ontario College Application Service (OCAS) data (pending)  

Included with the package are fictional data for both elementary (wide format) and secondary (long format) report card marks. 

```{r setup, warning=FALSE, message=FALSE}
library(obt)
library(dplyr)
```

```{r ele_rc}
head (ele_rc)
```

```{r sec_rc}
head (sec_rc)
```

