---
title: "Recoding Report Card Marks"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(obt)
library(dplyr)
```

The `obt` package contains a series of functions to recode report card data into commonly used variables. 

## Report Card Marks to Achievement Levels

```{r rc_ach_levels}

ele_rc |> 
  mutate(reading_levels = obt_recode_rc_to_levels(reading)) |> 
  select(school, id, reading, reading_levels) |> 
  slice_sample(n = 10)

```

## Report Card Marks to Met Standard / Did Not Meet Standard

```{r rc_to_standard}

sec_rc |> 
  mutate(final_ps = obt_recode_rc_L34(final)) |> 
  select(school, id, course_number, final, final_ps) |> 
  slice_sample(n = 10)

```


## Report Card Marks to Pass Fail
Results that are not the traditional alpha/numeric mark remain the same. For example ALT (alternative education), I (Insufficent) and NA (missing data). 

```{r rc_to_pass_fail}

ele_rc |> 
  mutate(read_pass_fail = obt_recode_rc_pass_fail(reading)) |> 
  select(school, id, reading, read_pass_fail) |> 
  arrange(read_pass_fail) |> 
  group_by(read_pass_fail) |> 
  slice_sample(n = 2)

```


## Report Letter Grade to Percent
This function will take a column that contains all alpha grades, or a combination of alpha and numeric grades, and convert the alpha grades to a numeric equivalent.  

**NOTE** - this may produce a warning message: *NAs introduced by coercion*. This means that any non-standard alpha mark has been converted to NA. 

* A+ = 90
* A  = 85"
* A- = 80
* B+ = 78
* B  = 75
* B- = 72"
* C+ = 68
* C  = 65
* C- = 62
* D+ = 58
* D = 55
* D- = 52
* D- = 52
* R  = 45
* All else = NA

```{r rc_alpha_to_numeric}

set.seed(168)

ele_rc |> 
  mutate(math_numeric = obt_recode_letter_percent(mathematics)) |> 
  select(school, id, mathematics, math_numeric) |> 
  slice_sample(n = 10)

```

